A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-01-22 manuscript.Rmd
add autolinked footnotes
remove typo

<<!-- the HTML comments, like this one, are meta comments, mainly describing the intent --->
<!-- each sentence below a heading summarizes what I want to say there --->
<!-- "Hands-on:" means concrete practical application, they roughly proceed from easy/familiar to hard/unfamiliar-->

@@

>>>>

<!-- the HTML comments, like this one, are meta comments, mainly describing the intent --->
<!-- each sentence below a heading summarizes what I want to say there --->
<!-- "Hands-on:" means concrete practical application, they roughly proceed from easy/familiar to hard/unfamiliar-->

@@

```{r, results='asis', echo=FALSE}
link_index()
```
